\documentclass{thesis}

\usepackage{amsmath}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage[table]{xcolor}
\usepackage[none]{hyphenat}

\author{Low Jia Ming}
\title{Driver Driving Behaviour Profiling Using Machine Learning Techniques}
\submissionyear{2016}
\submissionmonth{October}
\degree{BACHELOR OF COMPUTER SCIENCE}
\major{B.C.S (HONS) SOFTWARE ENGINEERING}
\session{Session 2016/2017}
\loadglsentries{myacronyms}

\begin{document}
\frontmatter
\makecoverandtitlepage
\copyrightpage
\declarationpage

\acknowledgements{First of all, I would like to thank my supervisor Dr. Poo Kuan Hoong for guiding me throughout this Final Year Project. I also appreciate the advice and comments given by my co-supervisor, Dr. Ian Tan. The most important thing is the mental and physical support of my family members and friends.
Lastly, I felt happy to have done this project. It is a great chance for me to learn new knowledge on machine learning. It is also my pleasure to have this chance to cooperate with my supervisor.}
\dedication{To my parents, my supervisors, and my friends.}

\abstractfromfile{sample-abstract}

{\clearpage\SingleSpacing
\tableofcontents\clearpage
\listoftables\clearpage
\listoffigures\clearpage}

%\prefacefromfile{sample-preface}

\mainmatter

\include{sample-chap-intro}
\include{chap-relatedwork}
\include{chap-theoritical}
\include{sample-chap-dummy}
\include{chap-implementation-plan}
\include{sample-chap-conclusion}

\appendix
%\include{sample-appen-manual}
\include{sample-appen-try}

\backmatter
\bibliography{references}
\printglossaries
{\SingleSpacing\printindex}
\bibliographyown{references}
\end{document}